### 2018-11-15 Sections/optical_encoding_of_quantum_information.tex
braket
CV

When encoding information optically, we needn't restrict ourselves to photon-number states. We also have a lot of flexibility to encode information in phase-space using continuous-variable (CV) states, where phase and amplitude relations encode quantum information \cite{bib:CahillGlauber69}.

In phase-space, the most common representations of optical states are in terms of quasi-probability functions\index{Quasi-probability functions}\footnote{The term `quasi-probablity' arises because in some regimes (for example, strictly non-negative $P$-functions), the function has a true probabilistic interpretation. However this interpretation breaks down for any negativity in the $P(\alpha)$, since negative probabilities have no meaningful classical interpretation.}:
\begin{itemize}\index{P-function}\index{Q-function}\index{Wigner function}
\item $P$-function: represents a state as a quasi-mixture of coherent states. When the $P$-function is strictly non-negative, it can be interpreted as a perfect classical mixture of coherent states. However, with any negativity this classical interpretation breaks down, hence `quasi'-probability. In general, the $P$-function representation for a state is not unique.
\begin{align}
\hat\rho = \int\!\!\!\int P(\alpha) \ket{\alpha}\bra{\alpha} d^2\alpha.
\end{align}
\item $Q$-function: represents a state in terms of its overlap with the complete set of all coherent states, which form an over-complete basis.
\begin{align}
Q(\alpha) = \frac{1}{\pi} \bra{\alpha}\hat\rho\ket{\alpha}.
\end{align}
\item Wigner function: also has a quasi-probability interpretation, and negativity is qualitatively associated with `quantumness'. The Wigner function of a state is unique, and isomorphic to the density operator, making it perhaps the most useful phase-space representation for quantum states of light.
\begin{align}
W(x,p) = \int e^{ips/\hbar} \left\langle{x-\frac{s}{2}}\right| \hat\rho \left|{x+\frac{s}{2}}\right\rangle ds.
\end{align}
\end{itemize}
These representations, whilst entirely equivalent to a photon-number basis representation, are far easier to work with for many types of states. Most notably, Gaussian states are conveniently represented and manipulated using phase-space representations.

@@

By manipulating these parameters, information can be encoded into coherent states. We could, for example, define two coherent states of opposite phase to represent qubit basis states,
\begin{align}
\ket{0} &\equiv \ket{\alpha}, \nonumber \\
\ket{1} &\equiv \ket{-\alpha}.
\end{align}
Note, however, that this representation for qubits is only approximate, since the two basis states are not perfectly orthogonal,
\begin{align}
\langle -\alpha|\alpha \rangle = e^{-2|\alpha|^2},
\end{align}
which is non-zero for any finite $\alpha$, whereas for ideal qubits we require \mbox{$\langle 0|1\rangle = 0$}. However, for large $\alpha$, $\ket{\pm\alpha}$ closely approximate orthogonality.

@@

@@

Another type of CV state, which can in fact encode quantum information, is superpositions of coherent states (colloquially known as `cat' states), with the encoding \cite{???},
\begin{align}
\ket{0} &\equiv \frac{1}{\sqrt{2(1+e^{-2|\alpha|^2})}} (\ket{\alpha}+\ket{-\alpha}) \nonumber \\
&= \ket{\mathrm{cat}_+(\alpha)},\nonumber \\
\ket{1} &\equiv \frac{1}{\sqrt{2(1-e^{-2|\alpha|^2})}}(\ket{\alpha}-\ket{-\alpha}) \nonumber \\
&= \ket{\mathrm{cat}_-(\alpha)}.
\end{align}
These two basis states contain strictly even or odd photon-number terms respectively (i.e they have well-defined parity), implying that, unlike coherent states, they are always orthogonal, regardless of amplitude,
\begin{align}
\langle\mathrm{cat}_+(\alpha)|\mathrm{cat}_-(\alpha)\rangle = 0 \,\,\forall\,\alpha,
\end{align}
making them directly appropriate for qubit encoding, even for weak coherent amplitudes.

@@

\subsubsection{Squeezed states}\index{Squeezed states}

Coherent state encoding can be regarded as encoding via the displacement operator, Eq.~(\ref{eq:disp_op}), which implements translations in phase-space. Alternately, we can encode via the squeezing operator, Eq.~(\ref{eq:sq_op}), which implements dilations about an axis in phase-space. Squeezing the vacuum state along the $\hat{x}$ or $\hat{p}$ directions yields two states that are approximately orthogonal for large squeezing amplitudes, as shown in Fig.~\ref{fig:squeezed_state_encoding}. Thus, with sufficient squeezing they can be used as a basis for approximately encoding a qubit. This encoding can be exploited for full universal quantum computing, as was introduced in Sec.~\ref{sec:CV_QC}.

>>>>

When encoding information optically, we needn't restrict ourselves to photon-number states (discrete variables\index{Discrete variables}). We also have a lot of flexibility to encode information in phase-space using continuous-variable (CV) states, where phase and amplitude relations encode quantum information \cite{bib:CahillGlauber69}. In this formalism, rather than expressing states in terms of photonic creation operators, $\hat{a}^\dag$, we represent them using phase-space position ($\hat{x}$) and momentum ($\hat{p}$) operators.

In phase-space, the most common method for visualising optical states is in terms of quasi-probability functions\index{Quasi-probability functions}\footnote{The term `quasi-probablity' arises because in some regimes (for example, strictly non-negative $P$-functions), the function has a true probabilistic interpretation. However this interpretation breaks down for any negativity in the $P(\alpha)$, since negative probabilities have no meaningful classical interpretation.}, of which there are a multitude. The best known quasi-probability representations are:
\begin{itemize}\index{P-function}\index{Q-function}\index{Wigner function}
\item $P$-function: represents a state as a quasi-mixture of coherent states. When the $P$-function is strictly non-negative, it can be interpreted as a perfect classical mixture of coherent states. However, with any negativity this classical interpretation breaks down, hence `quasi'-probability. In general, the $P$-function representation for a state is not unique.
\begin{align}
\hat\rho = \int\!\!\!\int P(\alpha) \ket{\alpha}\bra{\alpha} d^2\alpha.
\end{align}
\item $Q$-function: represents a state in terms of its overlap with the complete set of all coherent states, which form an over-complete basis.
\begin{align}
Q(\alpha) = \frac{1}{\pi} \braket{\alpha|\hat\rho|\alpha}.
\end{align}
\item Wigner function: also has a quasi-probability interpretation, and negativity is qualitatively associated with `quantumness'. The Wigner function of a state is unique, and isomorphic to the density operator, making it perhaps the most useful phase-space representation for quantum states of light.
\begin{align}
W(x,p) = \int e^{ips/\hbar} \left\langle x-\frac{s}{2}\right| \hat\rho \left|x+\frac{s}{2}\right\rangle ds.
\end{align}
\end{itemize}
These representations, whilst entirely equivalent to a photon-number basis representation, are far easier to work with for many types of states. Most notably, Gaussian states are conveniently represented and manipulated using phase-space representations.

@@

By manipulating these parameters, information can be encoded into coherent states. We could, for example, define two coherent states of opposite phase to represent qubit basis states,
\begin{align}
\ket{0} &\equiv \ket{\alpha}, \nonumber \\
\ket{1} &\equiv \ket{-\alpha}.
\end{align}
Note, however, that this representation for qubits is only approximate, since the two basis states are not perfectly orthogonal,
\begin{align}
\braket{-\alpha|\alpha} = e^{-2|\alpha|^2},
\end{align}
which is non-zero for any finite $\alpha$, whereas for ideal qubits we require \mbox{$\braket{0|1} = 0$}. However, for large $\alpha$, $\ket{\pm\alpha}$ closely approximate orthogonality.

@@

Coherent state encoding can be regarded as encoding via the displacement operator,
\begin{align}\label{eq:disp_op}
\hat{D}(\alpha) = \exp \left[\alpha\hat{a}^\dag - \alpha^*\hat{a}\right],
\end{align}
which implements translations in phase-space via the addition of coherent amplitude to a state. Coherent states are simply obtained as displaced vacuum states,
\begin{align}
\hat{D}(\alpha)\ket{0} = \ket{\alpha}.
\end{align}

@@

Another type of CV state, which can in fact encode quantum information, is superpositions of coherent states (colloquially known as `cat' states), with the encoding \cite{???},
\begin{align}
\ket{0} &\equiv \frac{1}{\sqrt{2(1+e^{-2|\alpha|^2})}} (\ket{\alpha}+\ket{-\alpha}) \nonumber \\
&= \ket{\mathrm{cat}_+(\alpha)},\nonumber \\
\ket{1} &\equiv \frac{1}{\sqrt{2(1-e^{-2|\alpha|^2})}}(\ket{\alpha}-\ket{-\alpha}) \nonumber \\
&= \ket{\mathrm{cat}_-(\alpha)}.
\end{align}
These two basis states contain strictly even or odd photon-number terms respectively (i.e they have well-defined parity), implying that, unlike coherent states, they are always orthogonal, regardless of amplitude,
\begin{align}
\braket{\mathrm{cat}_+(\alpha)|\mathrm{cat}_-(\alpha)} = 0 \,\,\forall\,\alpha,
\end{align}
making them directly appropriate for qubit encoding, even for weak coherent amplitudes.

@@

\subsubsection{Squeezed states}\index{Squeezed states}\label{sec:squeezed_enc}

In the same way that information can be encoded using the displacement operator, in the form of coherent states, we can encode information via the squeezing operator\index{Squeezing operator},
\begin{align}\label{eq:sq_op}
\hat{S}(\xi) = \exp\left[ \frac{1}{2}(\xi^*\hat{a}^2 - \xi{\hat{a}^{\dag 2}})\right],
\end{align}
where \mbox{$\xi  = r e^{i \varphi}$}, $r$ is known as the squeezing parameter\index{Squeezing parameter}, which will determine the magnitude of the squeezing and \mbox{$\varphi \in [0, 2\pi]$} denotes that axis along which the squeezing is taking place.

Graphically, in terms of their phase-space visualisation, squeezing implements dilations about a given axis. Strongly squeezing the vacuum state along the $\hat{x}$ or $\hat{p}$ directions yields two states that are approximately orthogonal for large squeezing amplitudes, as shown in Fig.~\ref{fig:squeezed_state_encoding}. Thus, with sufficient squeezing they can be used as a basis for approximating a qubit. This encoding can be exploited for full universal quantum computing, to be discussed in Sec.~\ref{sec:CV_QC}.

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.3\textwidth]{squeezed_state_encoding}
\captionspacefig \caption{Phase-space representation of two squeezed vacuum states, squeezed in the $\hat{x}$ (blue) and $\hat{p}$ (red) directions. In the limit of large squeezing these states become approximately orthogonal and may therefore approximate the encoding of a qubit.} \label{fig:squeezed_state_encoding}	
\end{figure}

In the CV picture, instead of representing states using photonic creation operators ($\hat a^\dag$), we express them in terms of the \textit{position} ($\hat x$)\index{Position operator} and \textit{momentum} ($\hat p$)\index{Momentum operator} operators, which are related to the creation and annihilation operators as,
\begin{align}
\hat x &=    \sqrt{\frac{\hbar}{2 \omega}}(\hat a + \hat a^\dag), \nonumber \\
\hat p &= -i \sqrt{\frac{\hbar  \omega}{2}}(\hat a - \hat a^\dag), 
\end{align}
where $\omega$ is the optical frequency\index{Optical!Frequency}. These operators obey the commutation relation,
\begin{align}
[\hat x, \hat p] = i \hbar.
\end{align}

The position and momentum operators represent the \textit{quadratures}\index{Quadratures} of a mode, and correspond to the real and imaginary components of a harmonic oscillator's\index{Harmonic oscillator} amplitude.

The \textit{position representation} of an optical state corresponds to expressing a state vector $\ket{\psi}$ in the position basis\index{Position basis representation},
\begin{align}
\ket{\psi} = \int \psi(x)\ket{x}\, dx,
\end{align}
where $\ket{x}$ are the eigenstates of the position operator. Here the wave-function in the position representation\index{Position basis representation} is defined as,
\begin{align}
\psi(x) = \braket{x|\psi}.
\end{align}
The state can similarly be expressed via a \textit{momentum representation}\index{Momentum basis representation},
\begin{align}
	\ket\psi = \int {\tilde\psi}(p) \ket{p}\, dp,
\end{align}
where,
\begin{align}
	{\tilde\psi}(p) = \braket{p|\psi}.
\end{align}

The quadrature eigenstates\index{Quadratures!Eigenstates} are mutually related to each other by a Fourier transform\index{Fourier transform},
\begin{align}
\ket{x} &= \frac{1}{\sqrt{\pi}} \int_{-\infty} ^\infty e^{-2 i x p} \ket{p} \,dp,\nonumber \\
\ket{p} &= \frac{1}{\sqrt{\pi}} \int_{-\infty} ^\infty e^{2 i x p} \ket{x} \,dx.
\end{align}

### 2018-11-15 Sections/physical_architectures_for_quantum_computing.tex
braket
ryser
Fixed up fig sizes for 1 col
CV

The permanent of a square matrix is defined as\index{Permanents},
\begin{align}\label{eq:permanent}
\mathrm{Per}(A) = \sum_{\sigma\in S_n} \prod_{i=1}^n A_{i,\sigma_i},
\end{align}
which sums over $n!$ terms (super-exponential), where $S_n$ is the symmetric group, the group of permutations on $n$ elements, of which there are $n!$. Note the similarity with the definition for the matrix determinant\index{Determinants}, defines identically, but with the addition of an alternating $\pm$-sign in the terms. Despite this similarity, determinants reside in \textbf{P}, with an efficient classical algorithm. For this reason, Fermionic sampling\index{Fermionic sampling} yields an easy computational problem, since Fermionic sampling differs only in replacing the permanent with the determinant. The best-known classical algorithm for evaluating has exponential runtime,
\begin{align}
	O(2^n n^2).
\end{align}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{BS_3_photon_combinatorics}
\caption{A linear optics interferometer $\hat{U}$, fed with 3 single-photon inputs, in modes 1, 2 and 3. To calculate the output amplitude of one photon in each of the modes 1, 2 and 3, we sum the amplitudes of all possible paths consistent with that output. This summation yields a \mbox{$3\times 3$} matrix permanent, given by Eq.~(\ref{eq:BS_3_ph_comb}).}\label{fig:BS_3_comb}	
\end{figure}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function SimulatePositiveP($\vec{P}$):
\begin{enumerate}
	\item for(m$\in$modes) \{
	\setlength{\itemindent}{0.2in}
	\item Randomly choose a sample $\alpha_m$ from probability distribution function $P_m(\alpha)$\index{Probability distribution function}.
	\setlength{\itemindent}{0in}
		\item \}
		\item Evolve the set of input coherent state samples through the linear optics network,
		\begin{align}
		\vec\beta = U\cdot\vec\alpha.
		\end{align}
	\item for(m$\in$modes) \{
	\setlength{\itemindent}{0.2in}
	\item The probability of measuring $n$ photons in the $m$th mode is given by the distribution,
	\begin{align}
	D_{m,n} &= |\langle\beta_m|n\rangle|^2 \nonumber \\
	&= e^{-|\beta_m|^2} \frac{{\beta_m}^{2n}}{n!}.
	\end{align}
	\item Choose $n$ from this distribution.
	\setlength{\itemindent}{0in}
	\item \}
	\item return($\vec{n}$).
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{Efficient classical algorithm for simulating any linear optics sampling problem whose input states have strictly non-negative $P$-functions, with output measured via photon-counting. $\vec{P}$ is the vector of $P$-functions for all modes.} \label{alg:positive_P_sim}
\end{table}

@@

In this picture, using squeezed states\index{Squeezed states} as a resource, qubits can be closely approximated by vacuum states squeezed in orthogonal directions, where the closeness of the approximation is determined by the squeezing parameter\footnote{In the limit of infinite squeezing the two orthogonally squeezed states becomes orthogonal, enabling the encoding of a genuine qubit.}.

A universal gate set can be constructed, enabling universal quantum computation to be implemented using this encoding. All the necessary elements may be readily implemented using present-day quantum optics technology and numerous CV quantum protocols have been demonstrated \cite{bib:RevModPhys.77.513}. Most notably, very large-scale CV cluster states have been experimentally prepared in the laboratory \cite{nickmenicucci???}.

In the CV picture, instead of representing states using photonic creation operators ($\hat a^\dag$), we express them in terms of the \textit{position} ($\hat x$)\index{Position operator} and \textit{momentum} ($\hat p$)\index{Momentum operator} operators, which can be expressed in terms of creation and annihilation operators as,
\begin{align}
\hat x &=    \sqrt{\frac{\hbar}{2 \omega}}(\hat a + \hat a^\dag), \nonumber \\
\hat p &= -i \sqrt{\frac{\hbar  \omega}{2}}(\hat a - \hat a^\dag), 
\end{align}
where $\omega$ is the optical frequency\index{Optical!Frequency}. These operators obey the commutation relation,
\begin{align}
[\hat x, \hat p] = i \hbar.
\end{align}

The position and momentum operators represent the quadratures\index{Quadratures} of a mode, and correspond to the real and imaginary components of a harmonic oscillator's\index{Harmonic oscillator} amplitude.

The position representation corresponds to expressing a state vector $\ket{\psi}$ in the position basis\index{Position basis representation},
\begin{align}
\ket{\psi} = \int \psi(x)\ket{x}\, dx,
\end{align}
where $\ket{x}$ are the eigenstates of the position operator. Here the wave function in the position representation\index{Position basis representation} is defined as,
\begin{align}
\psi(x) = \langle x|\psi\rangle.
\end{align}
The state can similarly be expressed in the momentum basis\index{Momentum basis representation},
\begin{align}
	\ket\psi = \int {\tilde\psi}(p) \ket{p}\, dp,
\end{align}
where,
\begin{align}
	{\tilde\psi}(p) = \langle p|\psi\rangle.
\end{align}

The quadrature eigenstates\index{Quadratures!Eigenstates} are mutually related to each other by a Fourier transform\index{Fourier transform},
\begin{align}
\ket{x} &= \frac{1}{\sqrt{\pi}} \int_{-\infty} ^\infty e^{-2 i x p} \ket{p} \,dp,\nonumber \\
\ket{p} &= \frac{1}{\sqrt{\pi}} \int_{-\infty} ^\infty e^{2 i x p} \ket{x} \,dx.
\end{align}

@@

Position and momentum eigenstates are orthogonal and may therefore be employed to encode a single qubit. However, these eigenstates have infinite energy. That is, they are infinitely squeezed in phase-space (Sec.~\ref{sec:squeezed}, \ref{sec:non_lin_opt})\index{Infinite squeezing}. However, position and momentum eigenstates can be closely approximated using finite, but large squeezing. The squeezed states\index{Squeezed states} in the two quadratures will now no longer be orthogonal, but will have overlap that asymptotes to zero as squeezing is increased. Thus, squeezed states can be used to approximate qubits using non-orthogonal basis states. Squeezed states may be prepared directly using a spontaneous parametric down-conversion (SPDC)\index{Spontaneous parametric down-conversion (SPDC)} process (Sec.~\ref{sec:single_phot_src}) \cite{bib:PhysRevLett.75.4337, bib:o2009photonic}. CV encoding using squeezed states is illustrated in phase-space in Fig.~\ref{fig:squeezed_state_encoding}.

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.3\textwidth]{squeezed_state_encoding}
\captionspacefig \caption{Phase-space representation of two squeezed vacuum states, squeezed in the $\hat{x}$ (blue) and $\hat{p}$ (red) directions. In the limit of large squeezing these states become approximately orthogonal and may therefore approximate the encoding of a qubit.} \label{fig:squeezed_state_encoding}	
\end{figure}

Squeezing simply corresponds to a dilation along a particular axis in phase-space. Squeezing is represented using the squeezing operator\index{Squeezing operator},
\begin{align}\label{eq:sq_op}
\hat{S}(\xi) = \exp\left[ \frac{1}{2}(\xi^*\hat{a}^2 - \xi{\hat{a}^{\dag 2}})\right],
\end{align}
where \mbox{$\xi  = r e^{i \varphi}$}, $r$ is known as the squeezing parameter\index{Squeezing parameter}, which will determine the size of the squeezing and \mbox{$\varphi \in [0, 2\pi]$} denotes that axis along which the squeezing is taking place.

\comment{How is squeezing implemented physically in the lab?}

@@

A phase-shifter\index{Phase-shifters}, implementing the unitary operation,
\begin{align}
\hat{R}(\theta) = e^{i\theta \hat{n}},
\end{align}
where \mbox{$\hat{n}=\hat a^\dag \hat a$} is the photon-number operator, rotates a state in phase-space by angle $\theta$, implementing the transformation between the position and momentum operators,
\begin{align}
\begin{pmatrix}
\hat x_{\theta}\\
\hat p_{\theta}
\end{pmatrix}
=
\begin{pmatrix}\cos\theta & \sin\theta \\
-\sin\theta & \cos\theta
\end{pmatrix}
\begin{pmatrix}
\hat x\\
\hat p
\end{pmatrix}.
\end{align}
It is evident upon inspection that this can be thought of as a single-qubit rotation in the position/momentum basis. \comment{Is it right that this is a single qubit operation in the x/p basis?}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{CV_bell_pair}
\captionspacefig \caption{Preparation of a CV Bell pair using a 50:50 beamsplitter to entangled two  squeezed states, squeezed in orthogonal directions in phase-space.}\label{fig:CV_bell_pair}	
\end{figure}

\comment{This is deterministic?}

@@

Measurement of CV states may be performed using homodyne detection\index{Homodyne detection} (Sec.~\ref{sec:homodyne}), which perform a projection along an arbitrary axis in phase-space, allowing $\hat{x}$ and $\hat{p}$, or any linear combination of the two, to be directly sampled.

Using a 50:50 beamsplitter to implement the reverse of Bell pair preparation (described previously in Sec.~\ref{sec:CV_bell_pairs}), one can construct a Bell analyser for performing projections in the Bell basis\index{Bell measurements}.

@@

In the position/momentum picture, the logical generalisations of the Pauli $\hat{X}$ and $\hat{Z}$ qubit gates may be thought of as displacements (Sec.~\ref{sec:non_lin_opt}) in the real and imaginary directions in phase-space \cite{bib:KokLovettBook},
\begin{align}
\hat{X}(s) \equiv \hat{D}(s)	, \, s\in\mathbb{R},\nonumber\\
\hat{Z}(t) \equiv \hat{D}(it), \, t\in\mathbb{R},
\end{align}
where,
\begin{align}\label{eq:disp_op}
\hat{D}(\alpha) = \exp \left[\alpha\hat{a}^\dag - \alpha^*\hat{a}\right],
\end{align}
is the phase-space displacement operator\index{Displacement operator}.

These have the action,
\begin{align}
	\hat{X}(s)\ket{x} &= \ket{x+s},\nonumber \\
	\hat{Z}(t)\ket{p} &= \ket{p+t}. 
\end{align}

The logical generalisation of the CZ gate is,
\begin{align}
\hat{U}_\mathrm{CZ} = e^{\frac{i}{2} \hat x_1 \hat x_2},
\end{align}
which transforms two-mode quadrature eigenstates as,
\begin{align}
\hat{U}_\mathrm{CZ} \ket{s}_1 \ket{t}_2 = e^{\frac{i}{2} s_1 t_2} \ket{s}_1\ket{t}_2.
\end{align}

@@

\startnormtable
\begin{table}[!htbp]
\begin{tabular}{ |c|c| } 
 \hline
 Qubit model gate &  CV equivalent \\ 
  \hline\hline
 Pauli $X$ & $\hat{X}(s) = \exp[-i s \hat p]$  \\ 
 Pauli $Z$ & $\hat{Z}(t) = \exp[i t \hat x]$  \\ 
 Phase gate & $\hat{P}(\eta) = \exp[i \eta \hat x^2]$ \\
Hadamard   & $\hat{F}=\exp[i \frac{\pi}{8}(\hat p^2+\hat x^2)]$ \\
CZ		   & $\hat{U}_\mathrm{CZ}= \exp[\frac{i}{2}\hat x_1 \hat x_2]$ \\
CNOT 	   & $\hat{U}_\mathrm{CNOT} = \exp[-2i\hat x_1 \hat p_2]$\\
\hline
\end{tabular}
\captionspacetab \caption{Logical generalisations of a universal gate set to the CV model for quantum computing.\label{tab:CV_gates}}
\end{table}
\startalgtable

@@

\comment{Describe the basic building blocks in a squeezed state cluster state architecture}

\comment{Please add any citations necessary for this entire section. Both theory and experimental work.}

>>>>

The permanent of a square matrix is defined as\index{Permanents},
\begin{align}\label{eq:permanent}
\mathrm{Per}(A) = \sum_{\sigma\in S_n} \prod_{i=1}^n A_{i,\sigma_i},
\end{align}
which sums over $n!$ terms (super-exponential), where $S_n$ is the symmetric group, the group of permutations on $n$ elements, of which there are $n!$. Note the similarity with the definition for the matrix determinant\index{Determinants}, defines identically, but with the addition of an alternating $\pm$-sign in the terms. Despite this similarity, determinants reside in \textbf{P}, with an efficient classical algorithm. For this reason, Fermionic sampling\index{Fermionic sampling} yields an easy computational problem, since Fermionic sampling differs only in replacing the permanent with the determinant. The best-known classical algorithm for evaluating permanents by \cite{bib:RyserAlg} has exponential runtime,
\begin{align}
	O(2^n n^2).
\end{align}

@@

\begin{figure}[!htbp]
\if 2\pubmode
	\includegraphics[clip=true, width=0.475\textwidth]{BS_3_photon_combinatorics}
\else
	\includegraphics[clip=true, width=0.6\textwidth]{BS_3_photon_combinatorics}
\fi
\caption{A linear optics interferometer $\hat{U}$, fed with 3 single-photon inputs, in modes 1, 2 and 3. To calculate the output amplitude of one photon in each of the modes 1, 2 and 3, we sum the amplitudes of all possible paths consistent with that output. This summation yields a \mbox{$3\times 3$} matrix permanent, given by Eq.~(\ref{eq:BS_3_ph_comb}).}\label{fig:BS_3_comb}	
\end{figure}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function SimulatePositiveP($\vec{P}$):
\begin{enumerate}
	\item for(m$\in$modes) \{
	\setlength{\itemindent}{0.2in}
	\item Randomly choose a sample $\alpha_m$ from probability distribution function $P_m(\alpha)$\index{Probability distribution function}.
	\setlength{\itemindent}{0in}
		\item \}
		\item Evolve the set of input coherent state samples through the linear optics network,
		\begin{align}
		\vec\beta = U\cdot\vec\alpha.
		\end{align}
	\item for(m$\in$modes) \{
	\setlength{\itemindent}{0.2in}
	\item The probability of measuring $n$ photons in the $m$th mode is given by the distribution,
	\begin{align}
	D_{m,n} &= |\braket{\beta_m|n}|^2 \nonumber \\
	&= e^{-|\beta_m|^2} \frac{{\beta_m}^{2n}}{n!}.
	\end{align}
	\item Choose $n$ from this distribution.
	\setlength{\itemindent}{0in}
	\item \}
	\item return($\vec{n}$).
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{Efficient classical algorithm for simulating any linear optics sampling problem whose input states have strictly non-negative $P$-functions, with output measured via photon-counting. $\vec{P}$ is the vector of $P$-functions for all modes.} \label{alg:positive_P_sim}
\end{table}

@@

In this picture, using squeezed states\index{Squeezed states} as a resource, qubits can be closely approximated by vacuum states squeezed in orthogonal directions, where the closeness of the approximation is determined by the squeezing parameter\footnote{In the limit of infinite squeezing the two orthogonally squeezed states becomes orthogonal, enabling the encoding of a genuine qubit.}. Squeezed state encoding of quantum information was introduced in Sec.~\ref{sec:squeezed_enc}.

A universal gate set can be constructed, enabling universal quantum computation to be implemented using this encoding. All the necessary elements may be readily implemented using present-day quantum optics technology and numerous CV quantum protocols have been demonstrated in recent years \cite{bib:RevModPhys.77.513}. Most notably, very large-scale CV cluster states have been experimentally prepared in the laboratory \cite{nickmenicucci???}.

@@

As discussed in Sec.~\ref{sec:squeezed_enc}, position and momentum eigenstates are orthogonal and may therefore be employed to encode a single qubit. However, these eigenstates have infinite energy. That is, they are infinitely squeezed in phase-space\index{Infinite squeezing}. However, position and momentum eigenstates can be closely approximated using finite, but strong squeezing. The squeezed states\index{Squeezed states} in the two quadratures will now no longer be orthogonal, but will have a small overlap that asymptotes to zero as squeezing is increased. Thus, squeezed states can be used to approximate qubits using non-orthogonal basis states. Squeezed states may be prepared directly using a spontaneous parametric down-conversion (SPDC)\index{Spontaneous parametric down-conversion (SPDC)} process (Sec.~\ref{sec:single_phot_src}) \cite{bib:PhysRevLett.75.4337, bib:o2009photonic}. CV encoding using squeezed states is illustrated in phase-space in Fig.~\ref{fig:squeezed_state_encoding}.

@@

A phase-shifter\index{Phase-shifters}, implementing the unitary operation,
\begin{align}
\hat{R}(\theta) = e^{i\theta \hat{n}},
\end{align}
where \mbox{$\hat{n}=\hat a^\dag \hat a$} is the photon-number operator\index{Photon-number operator}, rotates a state in phase-space by angle $\theta$, implementing the transformation between the position and momentum operators,
\begin{align}
\begin{pmatrix}
\hat x_{\theta}\\
\hat p_{\theta}
\end{pmatrix}
=
\begin{pmatrix}\cos\theta & \sin\theta \\
-\sin\theta & \cos\theta
\end{pmatrix}
\begin{pmatrix}
\hat x\\
\hat p
\end{pmatrix}.
\end{align}
It is evident upon inspection that this can be thought of as a single-qubit rotation in the position/momentum basis.

\comment{Is it right that this does single-qubit gates?}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{CV_bell_pair}
\captionspacefig \caption{Preparation of an (approximate) CV Bell pair using a 50:50 beamsplitter to entangled two states, squeezed in orthogonal directions in phase-space.}\label{fig:CV_bell_pair}	
\end{figure}

@@

Measurement of CV states may be performed using homodyne detection\index{Homodyne detection} (Sec.~\ref{sec:homodyne}), which performs a projection along an arbitrary axis in phase-space, allowing $\hat{x}$ and $\hat{p}$, or any linear combination of the two, to be directly sampled (i.e we can access the observables $\hat{x}_\theta$ and $\hat{p}_\theta$ for any $\theta$).

Using a 50:50 beamsplitter to implement the reverse of Bell pair preparation, one can construct a Bell analyser for performing projections in the Bell basis\index{Bell measurements}.

@@

In the position/momentum picture, the logical generalisations of the single-qubit Pauli $\hat{X}$ and $\hat{Z}$ gates may be thought of as displacements (Sec.~\ref{sec:non_lin_opt}) in the real and imaginary directions in phase-space \cite{bib:KokLovettBook},
\begin{align}
\hat{X}(s) \equiv \hat{D}(s)	, \, s\in\mathbb{R},\nonumber\\
\hat{Z}(t) \equiv \hat{D}(it), \, t\in\mathbb{R},
\end{align}
where $\hat{D}(\alpha)$ is the phase-space displacement operator\index{Displacement operator} from Eq.~(\ref{eq:disp_op}). These have the logical action,
\begin{align}
	\hat{X}(s)\ket{x} &= \ket{x+s},\nonumber \\
	\hat{Z}(t)\ket{p} &= \ket{p+t}. 
\end{align}

The logical generalisation of the CZ gate is,
\begin{align}
\hat{U}_\mathrm{CZ} = e^{\frac{i}{2} \hat x_1 \hat x_2},
\end{align}
which transforms two-mode quadrature eigenstates as,
\begin{align}
\hat{U}_\mathrm{CZ} \ket{s}_1 \ket{t}_2 = e^{\frac{i}{2} s_1 t_2} \ket{s}_1\ket{t}_2.
\end{align}
Intuitively, it's evident upon inspection of the form of the generalised CZ gate that it leaves logical basis state amplitudes unchanged, but adds state-dependent phases to basis states. Qualitatively, this is exactly what a regular CZ gate does in the space of two qubits, except that the basis is discrete rather than continuous.

@@

\startnormtable
\begin{table*}[!htbp]
\begin{tabular}{ |c|c|c| } 
 \hline
 Qubit model gate &  CV equivalent & Implementation \\ 
  \hline\hline
 Pauli $X$ & $\hat{X}(s) = \exp[-i s \hat p]$ & Coherent displacement \\ 
 Pauli $Z$ & $\hat{Z}(t) = \exp[i t \hat x]$ & Coherent displacement \\ 
 Phase gate & $\hat{P}(\eta) = \exp[i \eta \hat x^2]$ & Single-mode squeezing \& quadrature rotation \\
Hadamard   & $\hat{F}=\exp[i \frac{\pi}{8}(\hat p^2+\hat x^2)]$ & Phase-shift \\
CZ		   & $\hat{U}_\mathrm{CZ}= \exp[\frac{i}{2}\hat x_1 \hat x_2]$ & Two beamsplitters \& two squeezers \\
CNOT 	   & $\hat{U}_\mathrm{CNOT} = \exp[-2i\hat x_1 \hat p_2]$ & CZ \& Hadamards \\
\hline
\end{tabular}
\captionspacetab \caption{Logical generalisations of a universal gate set to the CV model for quantum computing using squeezed state encoding.\label{tab:CV_gates}}
\end{table*}
\startalgtable

@@

The CV model for quantum computation can be made universal by operating within the cluster state model. As discussed in Sec.~\ref{sec:CSQC}, the basic primitive from which the universality of cluster states arises is the single-qubit teleporter (Fig.~\ref{fig:single_qubit_teleporter}), which enables arbitrary quantum information to be teleported through the substrate state, accumulating the action of single- and two-qubit quantum gates in the processing, thereby building up a large, arbitrary computation. Thus, to demonstrate the universality of the CV model we must simply demonstrate an analogous circuit for single-mode CV state teleportation.

A circuit for a single-mode teleporter is shown in Fig.~\ref{fig:CV_teleporter}. Evidently, it is structurally almost identical to the standard single-qubit teleporter, just swapping out some operations for their direct CV equivalents.

This circuit has the desired property that, with classical feedforward and local corrections, we can teleport an arbitrary CV qubit state from one mode to another using the CV generalisation of the CZ gate.

\begin{figure}[!htbp]
	\begin{align}
		\Qcircuit @C=.7em @R=.4em @! {
		\lstick{\ket{\psi}} & \ctrl{1} & \qw & \meter & \hat{U}^\dag\hat{p}\hat{U} = m \\
		\lstick{\ket{0}_p} & \ctrl{0} & \gate{F} & \gate{X(m)} \cwx & \rstick{\hat{U}\ket\psi} \qw \\
		} \nonumber
	\end{align}
	\captionspacefig \caption{The single-mode teleporter using CV state encoding, structurally identical to an ordinary single-qubit teleporter, just substituting the operations with their respective CV generalisations.} \label{fig:CV_teleporter}\index{Continuous variables!Teleporter}
\end{figure}

Having demonstrated an equivalent single-mode teleporter, combined with the entangling generalised CZ gate, we have all we need to construct arbitrary measurement-based quantum computations using the generalised CZ gates as the primitive entangling operation for preparation of the substrate graph state.

% Fault-tolerance

\subsubsection{Fault-tolerance}\index{Fault-tolerance!Continuous variables}

\comment{To do}\cite{bib:menicucciFTCVCS}
